\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{url}
\usepackage{theorem}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{parskip}

\title{Bluff}
\author{Iniyan Joseph}

\begin{document}


\maketitle

\section{Introduction}
\section{Rules}
\begin{description}
    \subsection{Setup}
    \item Let there be $n$ players, $3\leq n\leq 7$.
    \item [Objective] Each player ($i$)'s objective is to dispose of all of their cards.
    \item Let there be a shared table into which players may discard cards.
    \item Let there be a global counter $\alpha$, defined as $\alpha_{0} = 1 \\ \alpha_{t} = (\alpha_{t-1} \bmod 13) + 1$.
    \item The game uses a standard deck of playing cards without jokers. 
    \subitem A deck consists of 52 cards consisting of 4 suites, with $13$ cards in each suite numbered from $1$ to $13$. 
    \item Initially, the cards are divided evenly between all players s.t. each player has $\lfloor\frac{52}{n}\rfloor$. The excess  $52 \bmod n$ cards are placed on the table
    \section{Defining a Player}
    \item Let the true distribution of cards for card $\alpha$ held be $T(\alpha)$. 
    \item Let the known distribution of cards for card $\alpha$ held be $K(\alpha)$
    \item Assume there are 4 cards of each number: $\forall_{a \in [1, 13]}\sum T(a) = 4$
    \section{Defining the table}
    \item Let the table be represented as player $i=0$, and the remaining players be $i=1, 2,..., n$
    \section{Defining a Turn}
    \item Play is conducted counter-clockwise, and no player may be skipped.
    \item In a turn, consider the distinct players $i$ and $j$.
    \item Let a turn ($t$) consist of the following sequence:
    \begin{enumerate}
        \item Player $i$ discards $p_t$ cards. $p_t \in [1,4]$
        \item Player $j$ may "call BS"
        \begin{enumerate}
            \item $\forall_{i\in p_t} type(i) = \alpha_t \iff $ $j$ must take the table
            \item $\exists_{i\in k_t} type(i) \neq \alpha_t \iff $ $i$ must take the table
            
            \subitem When $i$ takes the table, $\forall_{a \in [1, n]} \\ T(a)_i = T(a)_i + T(a)_0; T(a)_0 = 0$
        \end{enumerate}
    \end{enumerate}
    \section{The Problem}
    \paragraph{} We must find $P(T(\alpha_t)_{i} \geq p_t)$

\end{description}

$\mathbf{Equation~1}$ The number of solutions to the equation $\sum {a_r} = b, a_r \geq r = {{b - \sum r + |a| - 1}\choose{|a| - 1}}$\\
\section{Initial Game State}
The number of cards at the table can be seen as $\sum K(\alpha_t) + \sum T(\alpha_t) = 4$\\ s.t. $\forall_i K(\alpha_t)_i \geq K(\alpha_t)_i$\\
Applying equation 1, we may solve the equation with unknowns of $T$ for the n+1 players.\\
Let the function $\eta(S) = {{4-\sum S + |S| - 1}\choose{|S|-1}}$ where S is the set of known cards. % This must be expanded to consider the knowledge of 1 player 
\\
Let $K(\alpha_t)' = \{K(\alpha_t)_0, K_1, ... , K(\alpha_t)_{i-1}, p_t, K(\alpha_t)_{i+1}, ... , K(\alpha_t)_{n-1}, K(\alpha_t)_{n}\}$ \\ 
$P(T(\alpha_t)_{i} \geq p_t) = \frac{\eta(K')}{\eta(K)}$ 
\section{Additional Information}
To gain more information about players (and thus update the set $K$ to have non-zero values), there are exactly 2 cases in which information is revealed.

\begin{enumerate}
	\item If a player j calls "BS" and the player i was truthful, the condition holds that $\forall_{i\in p_t} type(i) = \alpha_t \iff $ $j$ must take the table. At this point, $K(\alpha_t)_j$ must increase by $p_t$, as $j$ is definitely holding their cards. 
	\item If you, the player, place a card of value $r$ in the the table, then until someone takes the table, $K(r)_0$ must increase by 1. Similarly, if the table is taken by another player $j$, those cards are now held by $j$ instead of $0$/the table. 
	
\end{enumerate} 
\section{Conclusion}

\end{document}